\documentclass[12pt, article]{article}
\usepackage{lmodern}

\input{head.tex}
\input{glossary.tex}

\usepackage{easylist}
\usepackage{hanging}
\usepackage{hyperref}
\usepackage{blindtext}
\usepackage{tipa}
\usepackage[left=2cm, top=2cm, bottom=2cm, right=1cm]{geometry}

\begin{document}

\input{cover.tex}
\pagenumbering{Roman}

\input{content.tex}


\begin{abstract}
An iron and steel factory at Bokaro employ about 30,000 workers, of whom, about 25,000 are
members of the Bokaro Iron \& Steel Workers’ Union, the only registered trade union operating
in the factory. The existing trade union and industrial relations law of the country recognizes
the right of the workers to organize into trade unions and confers upon registered trade unions
the usual civil and criminal immunities. The law does not obstruct trade unions from bargaining
collectively with their employers, nor does it prohibit their political activities. The management
of the factory is not hostile to the union or its leadership. The union also does not face problems
in the collection of subscription fees from its members. The union has been serious about
solving the problems facing its members: low wages, hazardous working conditions, long
hours of work, inadequate welfare amenities, unsatisfactory social security provisions,
absence of educational and recreational facilities in their housing colonies, inadequate
housing accommodation, absence of workers’ education and job insecurity. The union has
become very active and taken specific measures for solving these problems. It largely
succeeds in achieving its objectives.
\end{abstract}
\pagenumbering{arabic}
\input{body.tex}


% \nocite{*}
% % %Bibliogra*phy
%  \addcontentsline{toc}{section}{Bibliography}
%  \bibliographystyle{apalike}
%  \bibliography{bibliography}

\end{document}
